Relationships in the extremes and their influence on competition and coexistence

### 2021-09-30 paper/Paper.Rnw
rho not needed

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
fig2 <- readRDS(file="../results_numeric/fig2data.RDS")
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
se3 <- readRDS(file="../results_numeric/fig3maxse.RDS")
se4 <- readRDS(file="../results_numeric/fig4maxse.RDS")
@

@@

\begin{figure}
\includegraphics[width=.25\textwidth]{../results_figs/fig1_vertical.pdf}
\caption{Simple example of bivariate random variables with standard normal marginals showing
alternative patterns of association in the tails. A) is ``left-tail 
associated,'' B) is symmetric, and C) is ``right-tail associated'' noise. All three cases have 
the same Pearson correlation, $\rho = \Sexpr{rho}$, up to sampling variation, yet show very different 
patterns of association. We used asymmetrically tail associated cases which are perfectly 
correlated in the lower (A)  or upper (C) halves of the distributions, though it is also 
possible to generate asymmetrically tail associated noise with imperfect correlations in 
both halves of the distributions \citep{Ghosh_2020_AER,Nelsen2006}. The variables $(b_1,b_2)$ described in
the Introduction and Methods were obtained by generating 
noise as pictured and then multipling by $\sigma$ and adding $(\mu_1,\mu_2)$.\label{fig:noise}}
\end{figure}
%***DAN: Dan has edited this caption at least once.

>>>>

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
fig2 <- readRDS(file="../results_numeric/fig2data.RDS")
M <- readRDS(file="../results_numeric/M.RDS")
se3 <- readRDS(file="../results_numeric/fig3maxse.RDS")
se4 <- readRDS(file="../results_numeric/fig4maxse.RDS")
@

@@

\begin{figure}
\includegraphics[width=.25\textwidth]{../results_figs/fig1_vertical.pdf}
\caption{Simple example of bivariate random variables with standard normal marginals showing
alternative patterns of association in the tails. A) is ``left-tail 
associated,'' B) is symmetric, and C) is ``right-tail associated'' noise. All three cases have 
the same Pearson correlation, $\rho$, up to sampling variation, yet show very different 
patterns of association. We used asymmetrically tail associated cases which are perfectly 
correlated in the lower (A)  or upper (C) halves of the distributions, though it is also 
possible to generate asymmetrically tail associated noise with imperfect correlations in 
both halves of the distributions \citep{Ghosh_2020_AER,Nelsen2006}. The variables $(b_1,b_2)$ described in
the Introduction and Methods were obtained by generating 
noise as pictured and then multipling by $\sigma$ and adding $(\mu_1,\mu_2)$.\label{fig:noise}}
\end{figure}
%***DAN: Dan has edited this caption at least once.
